ghql
====

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

[![Build Status](https://travis-ci.org/ropensci/ghql.svg?branch=master)](https://travis-ci.org/ropensci/ghql)

`ghql` - general purpose GraphQL client

GraphQL - <http://graphql.org>

Examples of GraphQL APIs:

* [Github GraphQL API](https://developer.github.com/early-access/graphql/)

## Github Authentication

See <https://developer.github.com/early-access/graphql/guides/accessing-graphql/> for getting an OAuth token.

Store the token in a env var called `GITHUB_GRAPHQL_TOKEN`
before trying this pkg.

## Install

Development version

```{r eval=FALSE}
devtools::install_github("ropensci/ghql")
```

```{r}
library("ghql")
library("jsonlite")
```

## initialize client

```{r}
library("httr")
token <- Sys.getenv("GITHUB_GRAPHQL_TOKEN")
cli <- graphql(
  url = "https://api.github.com/graphql",
  headers = add_headers(Authorization = paste0("Bearer ", token))
)
```

## basic query

```{r}
cli$query('query { }')
cli$query_string
```

```{r}
cli$exec()
```


## more complex query

```{r}
cli$query('{
  repositoryOwner(login:"sckott") {
    repositories(first: 5, orderBy: {field:PUSHED_AT,direction:DESC}, isFork:false) {
      edges {
        node {
          name
          stargazers {
            totalCount
          }
        }
      }
    }
  }
}')
cli$query_string
```

```{r}
cli$exec()
```

## Meta

* Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
