ghql
====

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![R-check](https://github.com/ropensci/ghql/workflows/R-check/badge.svg)](https://github.com/ropensci/ghql/actions?query=workflow%3AR-check)
[![codecov.io](https://codecov.io/github/ropensci/ghql/coverage.svg?branch=master)](https://codecov.io/github/ropensci/ghql?branch=master)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/ghql)](https://github.com/r-hub/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/ghql)](https://cran.r-project.org/package=ghql)

`ghql` - a GraphQL client for R

GraphQL - <https://graphql.org>

Examples of GraphQL APIs:

* GitHub: <https://docs.github.com/en/graphql/guides/introduction-to-graphql>
* Opentargets: <https://genetics-docs.opentargets.org/technical-pipeline/graphql-api>
* Countries GraphQL API: <https://github.com/trevorblades/countries>

Other GraphQL R packages:

* [graphql][] - GraphQL query parser
* [gqlr][] - GraphQL server and query methods

## Install

CRAN version

```{r eval=FALSE}
install.packages("ghql")
```

Development version

```{r eval=FALSE}
remotes::install_github("ropensci/ghql")
```

```{r}
library("ghql")
library("jsonlite")
library("dplyr")
```

## Package Documentation

<https://docs.ropensci.org/ghql/>

## Meta

* Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.

[gqlr]: https://github.com/schloerke/gqlr
[graphql]: https://github.com/ropensci/graphql
[libgraphqlparser]: https://github.com/graphql/libgraphqlparser
